conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-06-13 paper/paper.Rmd
Updated implementation section

Conmat was built to predict at four settings: work, school, home, and other. The model is built to predict four separate models, one for each setting.
The model is a Poisson generalised additive model (GAM), predicting the count of contacts, with an offset of the log of participants. There are six terms to explain six key features of the relationship between ages, and optional terms for attendance at school or work, depending on which setting the model is predicting to.

@@

[#TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]

>>>>

`conmat` was built to predict at four settings: work, school, home, and other. 
The model is built to predict four separate models, one for each setting. [ #TODO a better way of saying the sentence prior? Predict four separate matrices?]
The model is a Poisson generalised additive model (GAM), predicting the count of contacts, with an offset of the log of participants. There are six terms to explain six key features of the relationship between ages, and optional terms for attendance at school or work, depending on which setting the model is predicting to.

@@

Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day. If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*. [ #TODO expected, predicted, or average?]

[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case.
